Testing atlantisom: generate census length and age comps

### 2019-05-02 TrueLengthAgeCompTest.Rmd
start age comp testing

---
title: "Testing atlantisom: example bottom trawl survey index"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

## Simulate a survey part 2: create a standard survey

This section uses the `atlantisom::create_survey()` and `atlantisom::sample_survey_biomass()` functions by creating a standard survey covering discrete areas, times, and species, and with both incomplete efficiency and some kind of length selectivity. We will apply this standard survey and compare it with true output as an example of the type of information that can be generated for assessment model performance testing.

>>>>

---
title: "Testing atlantisom: generate census length and age comps"
author: "Sarah Gaichas and Christine Stawitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
bibliography: "packages.bib"
---

@@

## Simulate a survey part 3: sample for length and age composition

This section uses the `atlantisom::create_survey()` and # script for using create_survey with the true numbers at age directly
# and then sample_fish to get a biolgical sample dataset
# from that dataset:
#   age samples from sample_ages
#   length samples from sample_lengths (TO BE WRITTEN)
#   weight samples from sample_weights (TO BE WRITTEN)
#   diet samples from sample_diet
 `atlantisom::sample_survey_biomass()` functions by creating a standard survey covering discrete areas, times, and species, and with both incomplete efficiency and some kind of length selectivity. We will apply this standard survey and compare it with true output as an example of the type of information that can be generated for assessment model performance testing.
